\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathrsfs}
\author{Dongrui Zhong, Bowen Li}
\title{Databases Project Phase 1: Proposal}
\addtolength{\voffset}{-1cm}
\addtolength{\hoffset}{-1cm}
\addtolength{\textwidth}{+2cm}
\addtolength{\textheight}{+3cm}

\begin{document}
\maketitle
\section*{1. Team}
Dongrui Zhong(Dzhong3), Bowen Li(bli26).

\section*{2. Target Domain}
Economical data ranges the whole United States. Data includes people size, different kinds of ratios(including education ratio, sex ratio age ratio etc.), median income, employments of all states and different years.

\section*{3. Questions}

\section*{4. Relational Data Model}

\section*{5. SQL Statement}

\section*{6. How to Load Values}
We will load data from the following website: https://census.gov and get the ".csv" or some other data type and load them into our own database. 

\section*{7. Report}
The final report can be a small website including frontend, backend and our database. Using the Model-View-Controller design pattern to design an interface satisfying people viewing some statistics of data, access of the backend whole or part dataset when login via password. Also, for a great part of the interface, we may implement some machine learning algorithms to do some prediction using data in the database.

\section*{8. Advanced Topics}
We may focus mainly on designing data mining(machine learning) algorithms and implementing an full stack website(interface) using Python and Django. 

\section*{9. Database Platform}
We may implement using Python and Django, and using SQLite as our Database. One of our computer is Macbook(1.1 GHz Intel Core M, 8 GB 1600 MHz DDR3, Intel HD Graphics 5300 1536 MB) and anther is Lenovo()

\end{document} 




